Title of the Master Thesis

### 2016-02-15 Master Thesis/synopsis.tex
WTF?
Remarks are numbered

\begin{remark}
If $L\subset M$ are intermediate fields of $\overline{K}/K$, which are finite over $K$, then $\sigma$ also induces bijections
\[ \operatorname{Spv}_\text{d}^{(1)}(L) \to \operatorname{Spv}_\text{d}^{(1)}(L'),\qquad \operatorname{Spv}_\text{d}^{(1)}(M) \to \operatorname{Spv}_\text{d}^{(1)}(M') \]
such that the following diagram commutes:
\[\begin{tikzcd}
\operatorname{Spv}_\text{d}^{(1)}(M) \rar["\sigma"]\dar & \operatorname{Spv}_\text{d}^{(1)}(M')\dar\\
\operatorname{Spv}_\text{d}^{(1)}(L) \rar["\sigma"'] & \operatorname{Spv}_\text{d}^{(1)}(L')
\end{tikzcd}\]
where the vertical maps are restrictions. Let $w\in\operatorname{Spv}_\text{d}^{(1)}(M),\ v=w|_L$ and $w'=\sigma(w),\ v'=\sigma(v)$. Then the following diagram commutes:
\[ \begin{tikzcd}
k(w') \rar["\varphi_w"] & k(w)\\
k(v') \rar["\varphi_v"']\uar[hook] & k(v)\uar[hook]
\end{tikzcd} \]
By limit process we see that $\sigma$ induces a bijection $\sigma: \operatorname{Spv}_\text{d}^{(1)}(\overline{K})\to \operatorname{Spv}_\text{d}^{(1)}(\overline{K'})$. Let $\overline{v}\in \operatorname{Spv}_\text{d}^{(1)}(\overline{K})$ and $G_{\overline{v}}\subset G_K$ be the decomposition group of $\overline{v}$. Then we have $\sigma(G_{\overline{v}}) = G_{\sigma(\overline{v})}$. Now it is easy to see that for every $g\in G_K$:
\[ \sigma(g\overline{v}) = \sigma(g)\sigma(\overline{v}) \]
\end{remark}

@@

\begin{lemma}\label{5.4}
Let $S\subset X_0$ be admissible and $P_0\in X_0\setminus S$. Then there exists a finite subset $T\subset X_0\setminus S$ with $P_0\in T$ such that the following map is injective:
\[ r_{S,T}:K^S \to\prod_{P\in T}k(P)^\times,\ x\mapsto(r_P(x))_{P\in T} \]
In this case, $\operatorname{coker}(r_{S,T})$ is free-by-finite.
\end{lemma}

>>>>

\begin{remark}\label{3.3}
If $L\subset M$ are intermediate fields of $\overline{K}/K$, which are finite over $K$, then $\sigma$ also induces bijections
\[ \operatorname{Spv}_\text{d}^{(1)}(L) \to \operatorname{Spv}_\text{d}^{(1)}(L'),\qquad \operatorname{Spv}_\text{d}^{(1)}(M) \to \operatorname{Spv}_\text{d}^{(1)}(M') \]
such that the following diagram commutes:
\[\begin{tikzcd}
\operatorname{Spv}_\text{d}^{(1)}(M) \rar["\sigma"]\dar & \operatorname{Spv}_\text{d}^{(1)}(M')\dar\\
\operatorname{Spv}_\text{d}^{(1)}(L) \rar["\sigma"'] & \operatorname{Spv}_\text{d}^{(1)}(L')
\end{tikzcd}\]
where the vertical maps are restrictions. Let $w\in\operatorname{Spv}_\text{d}^{(1)}(M),\ v=w|_L$ and $w'=\sigma(w),\ v'=\sigma(v)$. Then the following diagram commutes:
\[ \begin{tikzcd}
k(w') \rar["\varphi_w"] & k(w)\\
k(v') \rar["\varphi_v"']\uar[hook] & k(v)\uar[hook]
\end{tikzcd} \]
By limit process we see that $\sigma$ induces a bijection $\sigma: \operatorname{Spv}_\text{d}^{(1)}(\overline{K})\to \operatorname{Spv}_\text{d}^{(1)}(\overline{K'})$. Let $\overline{v}\in \operatorname{Spv}_\text{d}^{(1)}(\overline{K})$ and $G_{\overline{v}}\subset G_K$ be the decomposition group of $\overline{v}$. Then we have $\sigma(G_{\overline{v}}) = G_{\sigma(\overline{v})}$. Now it is easy to see that for every $g\in G_K$:
\[ \sigma(g\overline{v}) = \sigma(g)\sigma(\overline{v}) \]
\end{remark}

@@

\begin{lemma}\label{5.4}
Let $S\subset X_0$ be admissible. Then there exists a finite subset $T\subset X_0\setminus S$ such that the following map is injective:
\[ r_{S,T}:K^S \to\prod_{P\in T}k(P)^\times,\ x\mapsto(r_P(x))_{P\in T} \]
In this case, $\operatorname{coker}(r_{S,T})$ is free-by-finite.
\end{lemma}
